Move Schedules: Fast persistence computations in coarse dynamic settings\thanks{\textbf{Funding:} This work was partially supported by the National Science Foundation through grants CCF-2006661 and CAREER award DMS-1943758.}

### 2021-11-03 move_schedules.tex
arxiv version
Updates from Overleaf

% Authors: full names plus addresses.
\author{
	Matt Piekenbrock\thanks{Khoury College of Computer Sciences, Northeastern University.}
	\and Jose A. Perea\thanks{
	Department of Mathematics and Khoury College of Computer Sciences, Northeastern University.}
}

@@

% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={Fast Persistence Computations},
  pdfauthor={Matt Piekenbrock and Jose A. Perea}
}
\fi

>>>>

% Authors: full names plus addresses.
\author{
	Matthew Piekenbrock\thanks{Khoury College of Computer Sciences, Northeastern University.}
	\and Jose A. Perea\thanks{
	Department of Mathematics and Khoury College of Computer Sciences, Northeastern University.}
}

@@

% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={Move Schedules},
  pdfauthor={Matthew Piekenbrock and Jose A. Perea}
}
\fi
